Building socket-aware BPF programs

### 2018-11-01 paper/paper.tex
paper: Improve use cases, conclusion

@@

This paper describes the contribution of new BPF verifier functionality in the
Linux kernel to track references to kernel resources and uses these to provide
access to socket introspection capabilities from packet handling hooks. The
introduction of reference tracking logic into the verifier provides
useful base infrastructure for supporting acquire and release semantics for
kernel resources which may prove useful for other helpers in future, and the
socket lookup API makes the packet hooks more powerful to support use cases
such as stateful firewalling or conditional redirect based on the sockets that
are open on a system.

>>>>

This work was initially motivated by an attempt to re-think stateful
firewalling in the age of container networking, which is described in further
detail below. During the development process, another use case was identified
in the implementation of forwarding devices such as switches and routers, so
more detail is provided for this use case as well. Additional use cases are
expected to present themselves as BPF developers become more aware of the new
capabilities.

@@

Recent trends in the deployment of cloud applications using container images
through orchestrators such as Kubernetes have inspired a fresh look at the
approach used to provide networking and filtering capabilities in the network.
In light of these, this paper looks at the ability to perform stateful
firewalling through introspection of local kernel state. This paper describes
the contribution of new BPF verifier functionality in the Linux kernel to track
references to kernel resources and uses these to provide access to socket
attributes from packet handling hooks. The introduction of reference tracking
logic into the verifier provides useful base infrastructure for supporting
acquire and release semantics for kernel resources which may prove useful for
other helpers in future, and the socket lookup API makes the packet hooks more
powerful to support use cases ranging from stateful firewalling to handling
management traffic in network devices.
